---
title: "Oyster_Data_Validation"
output: html_document
---



```{r}
library(tidyverse)
library(readxl)
```

```{r}
make_mashable <- function(df, date){
  make_this <- df %>% 
    select(-c(X, ymin, ymax, sq)) %>%
    mutate(date = date)
  return(make_this)
}


stderr <- function(x) sd(x)/sqrt(length(x))

```


```{r}
#sample 1
vp1 <- read.csv("./data_check/clean_unknown_vp_6_15_22.csv") %>%
  make_mashable("2022-06-15")
vp1 <- vp1 %>% subset(cq <= 36.5) #account for positives in neg controls

vv1 <- read.csv("./data_check/clean_unknown_vv_6_15_22.csv") %>%
  make_mashable("2022-06-15")
vv1 <- vv1 %>% subset(cq <= 33.4) # account for positives in neg controls

raw1 <- rbind(vp1, vv1)

#sample 2
vp2 <- read.csv("./data_check/clean_unknown_vp_6_30_22.csv") %>%
  make_mashable("2022-06-30")
vv2 <- read.csv("./data_check/clean_unknown_vv_6_30_22.csv") %>%
  make_mashable("2022-06-30")
raw2 <- rbind(vp2, vv2)

#sample 3
vp3 <- read.csv("./data_check/clean_unknown_vp_7_14_22.csv") %>%
  make_mashable("2022-07-14")
vv3 <- read.csv("./data_check/clean_unknown_vv_7_14_22_cleaned.csv") %>%
  make_mashable("2022-07-14")
raw3 <- rbind(vp3, vv3)

#sample 4
vp4 <- read.csv("./data_check/clean_unknown_vp_7_27_22.csv") %>%
  make_mashable("2022-07-27")
vv4 <- read.csv("./data_check/clean_unknown_vv_7_27_22.csv") %>%
  make_mashable("2022-07-27")
raw4 <- rbind(vp4, vv4)

#sample 5
vp5 <- read.csv("./data_check/clean_unknown_vp_8_10_22.csv") %>%
  make_mashable("2022-08-10")
vv5 <- read.csv("./data_check/clean_unknown_vv_8_10_22.csv") %>%
  make_mashable("2022-08-10")
raw5 <- rbind(vp5, vv5)

#sample 6
vp6 <- read.csv("./data_check/clean_unknown_vp_8_23_22.csv") %>%
  make_mashable("2022-08-23")
vv6 <- read.csv("./data_check/clean_unknown_vv_8_23_22.csv") %>%
  make_mashable("2022-08-23")
raw6 <- rbind(vp6, vv6)

#sample 7
vp7 <- read.csv("./data_check/clean_unknown_vp_9_7_22.csv") %>%
  make_mashable("2022-09-07")
vv7 <- read.csv("./data_check/clean_unknown_vv_9_7_22.csv") %>%
  make_mashable("2022-09-07")
raw7 <- rbind(vp7, vv7)

#sample 8
vp8 <- read.csv("./data_check/clean_unknown_vp_9_20_22.csv") %>%
  make_mashable("2022-09-20")
vv8 <- read.csv("./data_check/clean_unknown_vv_9_20_22.csv") %>%
  make_mashable("2022-09-20")
raw8 <- rbind(vp8, vv8)

#sample 9
vp9 <- read.csv("./data_check/clean_unknown_vp_10_25_22.csv") %>%
  make_mashable("2022-10-25")
vv9 <- read.csv("./data_check/clean_unknown_vv_10_25_22.csv") %>%
  make_mashable("2022-10-25")
raw9 <- rbind(vp9, vv9)

#sample 10
vp10 <- read.csv("./data_check/clean_unknown_vp_11_2_22.csv") %>%
  make_mashable("2022-11-02")
vv10 <- read.csv("./data_check/clean_unknown_vv_11_2_22.csv") %>%
  make_mashable("2022-11-02")
raw10 <- rbind(vp10, vv10)

mash_all <- rbind(raw1, raw2, raw3, raw4, raw5, raw6, raw7, raw8, raw9, raw10)
```

Notes
FBC3 for Vv -- 2020-07-27 = likely biased (many wells failed on HEX)
2022-07-14 Vv assay = check front calculations, very low Ct values

```{r}
check_cy5 <- mash_all %>% subset(fluor == "Cy5")
```


```{r}
work <- mash_all

working <- work %>% select(c(fluor, sample, cq, target, date, dilution, container, treatment)) 


working %>% ggplot() +
  geom_jitter(aes(x = date, y = cq))
```
```{r}

only_hex <- working %>% subset(fluor == "HEX")

only_hex_no_na <- only_hex[!is.na(only_hex$cq), ] #pull all NAs for a proper average 

remove_38_up <- only_hex_no_na %>% subset(cq <= 38) #remove all values greater than or equal to 38

remove_38_up %>% ggplot() +
  geom_jitter(aes(x = target, y = cq, color = as.factor(dilution))) +
  facet_wrap(~date)

```


```{r}

averaging <- remove_38_up  %>%
  group_by(fluor, sample, dilution, date, target, container, treatment) %>%
  mutate(standerr = stderr(cq)) %>%
  ungroup() %>%
  mutate(high_std_err = case_when(
    .$standerr > 5 ~ "High",
    TRUE ~ "Not High")) 

averaging_for_real <-  averaging %>%
  select(-c(standerr, fluor)) %>%
 # group_by(sample, dilution, date, target, container, treatment) %>%
 # summarize_if(is.numeric, mean) %>%
  ungroup() %>%
  mutate(real_name = paste0(container, " ", treatment, " ", dilution))
```


```{r}
beautify <- averaging_for_real %>% 
  select(c(real_name, date, cq, target, treatment, container, dilution, sample)) %>%
  group_by(real_name, date, target, treatment, container, dilution, sample) %>%
  mutate(positive_tubes = n()) %>%
  ungroup() %>%
  select(-cq) %>%
  group_by(real_name, date, target, treatment, container, dilution, sample) %>%
  summarize_if(is.numeric, mean) %>%
  ungroup()
```



tubes <- c(3,3,3,3,3,3)
amount = c(0.1, 0.01, 0.001, 0.0001, 0.00001, 0.000001)

calc <- mpn(positive = vectorize, tubes = tubes, amount = amount)
return(calc$MPN)

}


```{r}
library(MPN)

dils <- c("-1", "-2", "-3", "-4", "-5", "-6") %>% as_tibble() %>% rename(dilution = value) 
dils$dilution <- as.integer(as.character(dils$dilution))

#MPN calcul-o-maker-izer 
find_mpn <- function(df, date_name, target_name, sample_name){
  mpn_make <- beautify %>% 
    subset(date == date_name & target == target_name & sample == sample_name)
  
find <- mpn_make %>% select(positive_tubes, dilution) %>% 
  right_join(dils) %>% 
  mutate(dilution = abs(dilution))

find <- find[order(as.numeric(as.character(find$dilution))),]
vectorize <- as.vector(find$positive_tubes)
vectorize[is.na(vectorize)] <- 0
  
tubes <- c(3,3,3,3,3,3)
amount = c(0.1, 0.01, 0.001, 0.0001, 0.00001, 0.000001)
  
calc <- mpn(positive = vectorize, tubes = tubes, amount = amount)

make_this <- calc$MPN %>%
  as_tibble() %>%
  mutate(date = date_name,
         sample = sample_name,
         target = target_name,
         tube_minus1 = vectorize[1],
         tube_minus2 = vectorize[2],
         tube_minus3 = vectorize[3],
         tube_minus4 = vectorize[4],
         tube_minus5 = vectorize[5],
         tube_minus6 = vectorize[6])


     return(make_this)

}
```

```{r}
  
tubes <- c(3,3,3,3,3,3)
amount = c(0.1, 0.01, 0.001, 0.0001, 0.00001, 0.000001)

mpn_make <- beautify %>% 
    subset(date == "2022-07-14" & target == "Vv" & sample == "FBT3")
vectorize <- as.vector(mpn_make$positive_tubes)
  length(vectorize) <- 6
  vectorize[is.na(vectorize)] <- 0
  
  calc <- mpn(positive = vectorize, tubes = tubes, amount = amount)
  
make_this <- calc$MPN %>%
  as_tibble()

tubes <- c(3,3,3,3,3,3)
amount = c(0.1, 0.01, 0.001, 0.0001, 0.00001, 0.000001)
```


```{r}
mpn_make <- beautify %>% 
    subset(date == "2022-06-15" & target == "Vv" & sample == "FBT3")

find <- mpn_make %>% select(positive_tubes, dilution) %>% 
  right_join(dils) %>% 
  mutate(dilution = abs(dilution))

find <- find[order(as.numeric(as.character(find$dilution))),]
vectorize <- as.vector(find$positive_tubes)
vectorize[is.na(vectorize)] <- 0
  
  calc <- mpn(positive = vectorize, tubes = tubes, amount = amount)
  
make_this <- calc$MPN %>%
  as_tibble()
```

```{r}
#Event 1 6/15/22
vp1_mpn <- find_mpn(beautify, "2022-06-15", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vp", "FCC3"))

vv1_mpn <- find_mpn(beautify, "2022-06-15", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-06-15", "Vv", "FCC3"))

#Event 2 6/30/22
vp2_mpn <- find_mpn(beautify, "2022-06-30", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vp", "FCC3"))

vv2_mpn <- find_mpn(beautify, "2022-06-30", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-06-30", "Vv", "FCC3"))

#Event 3 7/14/22
vp3_mpn <- find_mpn(beautify, "2022-07-14", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vp", "FCC3"))

vv3_mpn <- find_mpn(beautify, "2022-07-14", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-07-14", "Vv", "FCC3"))

#Event 4 7/24/22
vp4_mpn <- find_mpn(beautify, "2022-07-27", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vp", "FCC3"))

vv4_mpn <- find_mpn(beautify, "2022-07-27", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-07-27", "Vv", "FCC3"))


#Event 5 8/10/22
vp5_mpn <- find_mpn(beautify, "2022-08-10", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vp", "FCC3"))

vv5_mpn <- find_mpn(beautify, "2022-08-10", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-08-10", "Vv", "FCC3"))

#Event 6 8/23/22
vp6_mpn <- find_mpn(beautify, "2022-08-23", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vp", "FCC3"))

vv6_mpn <- find_mpn(beautify, "2022-08-23", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-08-23", "Vv", "FCC3"))

#Event 7 9/7/22
vp7_mpn <- find_mpn(beautify, "2022-09-07", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vp", "FCC3"))

vv7_mpn <- find_mpn(beautify, "2022-09-07", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-09-07", "Vv", "FCC3"))

#Event 8 9/20/22
vp8_mpn <- find_mpn(beautify, "2022-09-20", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vp", "FCC3"))

vv8_mpn <- find_mpn(beautify, "2022-09-20", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-09-20", "Vv", "FCC3"))

#Event 9 10/25/22
vp9_mpn <- find_mpn(beautify, "2022-10-25", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vp", "FCC3"))

vv9_mpn <- find_mpn(beautify, "2022-10-25", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-10-25", "Vv", "FCC3"))

#Event 10 11/2/22
vp10_mpn <- find_mpn(beautify, "2022-11-02", "Vp", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vp", "FCC3"))

vv10_mpn <- find_mpn(beautify, "2022-11-02", "Vv", "FBT1") %>% 
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FBT2")) %>% 
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FBT3")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FBC1")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FBC2")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FBC3")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FCT1")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FCT2")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FCT3")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FCC1")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FCC2")) %>%
  rbind(find_mpn(beautify, "2022-11-02", "Vv", "FCC3"))
```


```{r}
clean_mpn <- rbind(vp1_mpn, vv1_mpn, vp2_mpn, vv2_mpn, vp3_mpn, vv3_mpn, vp4_mpn, vv4_mpn, vp5_mpn, vv5_mpn, vp6_mpn, vv6_mpn, vp7_mpn, vv7_mpn, vp8_mpn, vv8_mpn, vp9_mpn, vv9_mpn, vp10_mpn, vv10_mpn)  %>%
  mutate(tag = substr(sample, 1,3))

y_lab <- expression("MPN g"~ phantom()^{-1})


clean_mpn %>% ggplot() +
  geom_boxplot(aes(x = target, y = value, fill = tag)) +
  facet_wrap(~date)


```

```{r}
write.csv(clean_mpn, "./adjust_mpns.csv")
```

```{r}
return <- read.csv("./adjusted_mpns.csv")

clean_mpn <- return
```


```{r}
only_vp <- clean_mpn %>% subset(target == "Vp")
only_vv <- clean_mpn %>% subset(target == "Vv") %>% mutate(pull = case_when(
  .$date == "2022-06-15" & .$sample == "FBT3" ~ "toss",
  .$date == "2022-06-15" & .$sample == "FCT3" ~ "toss",
  .$date == "2022-06-15" & .$sample == "FBC1" ~ "toss",
  TRUE ~ "keep")) %>%
  subset(pull == "keep")

only_vp %>% ggplot() +
  geom_boxplot(aes(x = target, y = value, fill = tag)) +
  facet_wrap(~date) +
  scale_y_log10(labels = scales::comma) +
  theme_bw() +
  xlab("Target") +
  ylab(y_lab)+
  labs(fill = "Sample Type")

only_vp %>% ggplot() +
  geom_boxplot(aes(x = date, y = value, fill = tag)) +
  scale_y_log10(labels = scales::comma) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) + 
  xlab("Date") +
  ylab(y_lab)+
  labs(fill = "Sample Type")

only_vv %>% ggplot() +
  geom_boxplot(aes(x = target, y = value, fill = tag)) +
  facet_wrap(~date) +
  scale_y_log10(labels = scales::comma) +
  theme_bw() +
  xlab("Target") +
  ylab(y_lab)+
  labs(fill = "Sample Type")

only_vv %>% ggplot() +
  geom_boxplot(aes(x = date, y = value, fill = tag)) +
  scale_y_log10(labels = scales::comma) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) + 
  xlab("Date") +
  ylab(y_lab)+
  labs(fill = "Sample Type")

```


```{r, fig.width=7, fig.height=7}
y_lab <- expression("MPN g"~ phantom()^{-1})

clean_mpn2 <- clean_mpn %>%  mutate(pull = case_when(
  .$date == "2022-06-15" & .$target == "Vv" & .$sample == "FBT3" ~ "toss",
  .$date == "2022-06-15" & .$target == "Vv" & .$sample == "FCT3" ~ "toss",
  .$date == "2022-06-15" & .$target == "Vv" & .$sample == "FBC1" ~ "toss",
  TRUE ~ "keep")) %>%
  subset(pull == "keep")

clean_mpn2 %>% ggplot() +
  geom_point(aes(x = as.Date(date), y = value, color = target)) +
    geom_line(aes(x = as.Date(date), y = value, color = target, group = target)) +
  facet_wrap(~sample, ncol = 3)+
  scale_y_log10(labels = scales::comma)+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
  xlab("Sample Date") +
  ylab(y_lab)+
  labs(color = "Target")
```

```{r}
write.csv(clean_mpn, "./data_check/clean_mpn.csv")
```


```{r}
container <- clean_mpn2 %>% mutate(tag = recode(tag,
                                               "FBT" = "FB",
                                               "FBC" = "FB",
                                               "FCC" = "FC",
                                               "FCT" = "FC")) %>%
  select(c(value, date, tag, target))

container %>% ggplot() +
  geom_boxplot(aes(x = date, y = log10(value), fill = tag))


container2 <- container %>% group_by(date, tag, target) %>%
  summarize_if(is.numeric, mean) %>%
  ungroup() %>%
  mutate(log10_mpn = log10(value))%>%
  mutate(target = recode(target,
                         "Vp" = "V. parahaemolyticus",
                         "Vv" = "V. vulnificus")) %>%
  mutate(tag = recode(tag,
                      "FB" = "Floating Bag",
                      "FC" = "Floating Cage"))

container2$date <- as.Date(as.character(container2$date))
```


```{r, fig.width=8}
y_lab2 <- expression("Log10 MPN g"~ phantom()^{-1})


container2 %>% ggplot() +
  geom_line(aes(x = date, y = log10_mpn, color = target, 
                group = interaction(tag, target), linetype = tag), size = 1) +
  geom_point(aes(x = date, y = log10_mpn, color = target, 
                group = interaction(tag, target)), size = 1.5)+
  theme_bw()+
  xlab("Date") +
  ylab(y_lab2) +
  labs(color = "Target",
       linetype = "Container Type")+
  theme(legend.position = "bottom")
```

```{r}
container3 <- clean_mpn2 %>% mutate(tag = recode(tag,
                                               "FBT" = "T",
                                               "FBC" = "C",
                                               "FCC" = "C",
                                               "FCT" = "T")) %>%
  select(c(value, date, tag, target))

container3 %>% ggplot() +
  geom_boxplot(aes(x = date, y = log10(value), fill = tag))


container4 <- container3 %>% group_by(date, tag, target) %>%
  summarize_if(is.numeric, mean) %>%
  ungroup() %>%
  mutate(log10_mpn = log10(value))%>%
  mutate(target = recode(target,
                         "Vp" = "V. parahaemolyticus",
                         "Vv" = "V. vulnificus")) %>%
  mutate(tag = recode(tag,
                      "T" = "2 hours",
                      "C" = "Control"))

container4$date <- as.Date(as.character(container4$date))
```

```{r}
container4 %>% ggplot() +
  geom_line(aes(x = date, y = log10_mpn, color = target, 
                group = interaction(tag, target), linetype = tag), size = 1) +
  geom_point(aes(x = date, y = log10_mpn, color = target, 
                group = interaction(tag, target)), size = 1.5)+
  theme_bw()+
  xlab("Date") +
  ylab(y_lab2) +
  labs(color = "Target",
       linetype = "Container Type")+
  theme(legend.position = "bottom")
```





