---
title: "temp_processing"
output: html_document
---


```{r}
library(tidyverse)
library(readxl)
library(ggthemes)
library(ggforce)
library(SciViews)
```

```{r}
raw1 <- read_excel("./temp_runs/sal_3_temp_30_iron_normal.xlsx", 2) %>%
  select(-c(...99))

raw2<- read_excel("./temp_runs/sal_3_temp_34_iron_normal.xlsx", 2) %>%
  select(-c(...99))

raw3<- read_excel("./temp_runs/sal_3_temp_36_iron_normal.xlsx", 2) %>%
  select(-c(...99))

raw4<- read_excel("./temp_runs/sal_3_temp_38_iron_normal.xlsx", 2) %>%
  select(-c(...99))

raw5<- read_excel("./temp_runs/sal_3_temp_40_iron_normal.xlsx", 2) %>%
  select(-c(...99))

raw6<- read_excel("./temp_runs/sal_3_temp_24_iron_normal.xlsx", 2) %>%
  select(-c(...99))

raw7<- read_excel("./temp_runs/sal_3_temp_32_iron_normal.xlsx", 2) %>%
  select(-c(...99))

raw8 <- read_excel("./temp_runs/sal_3_temp_28_iron_normal.xlsx", 2) %>%
  select(-c(...91))

raw9 <- read_excel("./temp_runs/sal_3_temp_26_iron_normal.xlsx", 2) %>%
  select(-c(...83))
```

```{r}
pull_sides <- raw8 %>% select(-contains("Blank")) %>%
  select(-contains("Ctrl")) %>%
  select(-contains("A0")) %>% #Remove A rows 
  select(-contains("A1")) %>%
  select(-contains("H0")) %>% #Remove H rows 
  select(-contains("H1"))

pull_sides[pull_sides<0] <- 0
pull_sides <- pull_sides %>% rename(
  reading = "Reading",
  time = "avg. time [s]")

names(pull_sides)[3:68] <- str_sub(names(pull_sides)[3:68],end = -11)

pivot <- pull_sides %>% pivot_longer(cols = -c(reading, time), names_to = "strain", values_to = "od")

pivot  <- pivot[!is.na(pivot$reading),]

clean_8 <- pivot %>% group_by(reading, time, strain) %>%
  summarise_if(is.numeric, mean) %>%   
  ungroup() %>%
  mutate(time = time / 3600)


clean_8 <- clean_8[!(clean_8$strain == "Un"), ]

```



```{r}

make_the_thing <- function(df) {
pull_sides <- df %>% select(-contains("Blank")) %>%
  select(-contains("Ctrl")) %>%
  select(-contains("A0")) %>% #Remove A rows 
  select(-contains("A1")) %>%
  select(-contains("H0")) %>% #Remove H rows 
  select(-contains("H1"))
 
pull_sides[pull_sides<0] <- 0
pull_sides <- pull_sides %>% rename(
  reading = "Reading",
  time = "avg. time [s]")


names(pull_sides)[3:62] <- str_sub(names(pull_sides)[3:62],end = -11)

pivot <- pull_sides %>% pivot_longer(cols = -c(reading, time), names_to = "strain", values_to = "od")

pivot  <- pivot[!is.na(pivot$reading),]

clean <- pivot %>% group_by(reading, time, strain) %>%
  summarise_if(is.numeric, mean) %>%   
  ungroup() %>%
  mutate(time = time / 3600)

return(clean)

}

stderr <- function(x) sd(x)/sqrt(length(x))


make_1 <- make_the_thing(raw1) %>%
  mutate(temp = "30 C")

make_2 <- make_the_thing(raw2) %>%
  mutate(temp = "34 C")

make_3 <- make_the_thing(raw3) %>%
  mutate(temp = "36 C")

make_4 <- make_the_thing(raw4) %>%
  mutate(temp = "38 C")

make_5 <- make_the_thing(raw5) %>%
  mutate(temp = "40 C")

make_6 <- make_the_thing(raw6) %>%
  mutate(temp = "24 C")

make_7 <- make_the_thing(raw7) %>%
  mutate(temp = "32 C")

make_8 <- clean_8 %>%
  mutate(temp = "28 C")

make_9 <- make_the_thing(raw9) %>%
  mutate(temp = "26 C")


make_all_the_things <- rbind(make_1, make_2, make_3, make_4, make_5, make_6, make_7, make_8, make_9) %>%
  mutate(strain = recode(strain,
                         "ATC" = "ATCC"))

make_all_the_things$strain <- factor(make_all_the_things$strain, levels = c("551", "580", "507", "ATCC"))
```

```{r}
write.csv(make_all_the_things, "all_temp.csv")
```


```{r, fig.width=10}
cols = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F", "#E5C494", "#B3B3B3", "red")

p1 <- make_all_the_things %>% ggplot() +
  geom_line(aes(x = time, y = od, color = strain), size = 1) +
  facet_wrap(~temp) +
  theme_bw() +
  xlab("Time (hrs)")+
  ylab("Optical Density (600nm)")+
  labs(color = "Strain") +
  ggtitle("V. alginolyticus strains vs. temperature")+
    scale_color_manual(values = cols)


p1
```
```{r}
only_551 <- make_all_the_things %>% subset(strain == "551")

only_507 <- make_all_the_things %>% subset(strain == "507")

only_580 <- make_all_the_things %>% subset(strain == "580")

only_ATCC <- make_all_the_things %>% subset(strain == "ATCC")

```

```{r}
only_551 %>% ggplot() +
  geom_line(aes(x = time, y = od, color = temp), size =1) +
  theme_bw() +
  xlab("Time (hrs)")+
  ylab("Optical Density (600nm)")+
  labs(color = "Strain") +
  ggtitle("V. alginolyticus strain 551 vs. temperature")+
    scale_color_manual(values = cols)

only_580 %>% ggplot() +
  geom_line(aes(x = time, y = od, color = temp), size =1) +
  theme_bw() +
  xlab("Time (hrs)")+
  ylab("Optical Density (600nm)")+
  labs(color = "Strain") +
  ggtitle("V. alginolyticus strain 580 vs. temperature")+
    scale_color_manual(values = cols)

only_507 %>% ggplot() +
  geom_line(aes(x = time, y = od, color = temp), size =1) +
  theme_bw() +
  xlab("Time (hrs)")+
  ylab("Optical Density (600nm)")+
  labs(color = "Strain") +
  ggtitle("V. alginolyticus strain 507 vs. temperature")+
    scale_color_manual(values = cols)

only_ATCC %>% ggplot() +
  geom_line(aes(x = time, y = od, color = temp), size =1) +
  theme_bw() +
  xlab("Time (hrs)")+
  ylab("Optical Density (600nm)")+
  labs(color = "Strain") +
  ggtitle("V. alginolyticus strain ATCC vs. temperature")+
    scale_color_manual(values = cols)
```


```{r, fig.width=10}
lag_phase <- make_all_the_things %>% subset(od >= 0.05 & od < 0.15)
stat_phase <- make_all_the_things %>% subset(time >= 14.5 & od < 15.5)
cols = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02", "#A6761D", "#666666", "red") #brewer dark2

just_ave_lag <- lag_phase %>% select(temp, time, strain) %>%
  group_by(temp, strain) %>%
  mutate(lag_error = stderr(time),
         lag_n = n()) %>%
  summarize_if(is.numeric, mean) %>%
  ungroup() %>%
  rename(lag_time = time) %>%
  mutate(max_lag = lag_time + lag_error,
         min_lag = lag_time - lag_error)


# lag_phase %>% ggplot() +
#   geom_boxplot(aes(x = strain, y = time, fill = temp)) +
#   geom_vline(xintercept = 1.5, linetype = "dashed")+
#   geom_vline(xintercept = 2.5, linetype = "dashed")+
#   geom_vline(xintercept = 3.5, linetype = "dashed")+
#   theme_classic() +
#   xlab("Strain ID")+
#   ylab("Time (hrs)") +
#   ggtitle("Duration of Lag Phase vs. Temperature (C)")+
#   labs(fill = "Temperature (C)")+
#   scale_fill_manual(values = cols)
# 
# stat_phase %>% ggplot() +
#   geom_boxplot(aes(x = strain, y = od, fill = temp))+
#   geom_vline(xintercept = 1.5, linetype = "dashed")+
#   geom_vline(xintercept = 2.5, linetype = "dashed")+
#   geom_vline(xintercept = 3.5, linetype = "dashed")+
#   theme_classic() +
#   xlab("Strain ID")+
#   ylab("Optical Density 600nm") +
#   ggtitle("Stationary Phase Optical Density vs. Temperature (C)")+
#   labs(fill = "Temperature (C)")+
#   scale_fill_manual(values = cols)


```


```{r}
make_all_the_things<- make_all_the_things %>% left_join(just_ave_lag)
make_all_the_things$strain <- factor(make_all_the_things$strain, levels = c("551", "580", "507", "ATCC"))
```
```{r}
#serious GR equation
library(SciViews)
x <- make_all_the_things %>%
  subset(od >= 0.1 & od <= 0.75) %>%
  select(-lag_time)

x$reading <- as.numeric(as.character(x$reading))
x <- x[!(x$reading < 50), ]

binned <- x %>% group_by(strain, temp) %>%
  mutate(total_hits = n()) %>%
  ungroup() %>%
  mutate(total_min = total_hits*2.3,
         reading_min = reading * 2.3)


early_log <- binned %>% select(-total_hits, -total_min, -reading, -time) %>%
  subset(od <= 0.2) %>%
  group_by(strain, temp) %>%
  mutate(early_od_err = stderr(od),
         early_time_err = stderr(reading_min)) %>%
  summarize_if(is.numeric, mean) %>%
  ungroup() %>%
  rename(early_log_od = od, 
         early_log_min = reading_min) %>%
  mutate(early_od_max = early_log_od + early_od_err,
         early_od_min = early_log_od - early_od_err,
         early_time_max = early_log_min + early_time_err,
         early_time_min = early_log_min - early_time_err)

#late_log <- binned %>% select(-total_hits, -total_min, -reading, -time) %>%
#  subset(od > 0.6) %>%
#  group_by(strain, temp) %>% mutate(nn = n())

late_log <- binned %>% select(-total_hits, -total_min, -reading, -time) %>%
  subset(od > 0.65) %>%
  group_by(strain, temp) %>%
  mutate(late_od_err = stderr(od),
         late_time_err = stderr(reading_min)) %>%
  summarize_if(is.numeric, mean) %>%
  ungroup() %>%
  rename(late_log_od = od,
         late_log_min = reading_min) %>%
    mutate(late_od_max = late_log_od + late_od_err,
         late_od_min = late_log_od - late_od_err,
         late_time_max = late_log_min + late_time_err,
         late_time_min = late_log_min - late_time_err)

gr_df <- left_join(early_log, late_log)

gr_df <- gr_df %>% mutate(time_diff = late_log_min - early_log_min) %>%
  mutate(ln_late_log = ln(late_log_od)) %>%
  mutate(ln_early_log = ln(early_log_od)) %>%
  mutate(gr_constant = ((ln_late_log) - (ln_early_log)) / time_diff) %>%
  mutate(gr = 0.6931 / gr_constant)

gr_df_max <- gr_df %>% mutate(time_diff_max = late_time_max - early_time_max) %>%
  mutate(ln_late_log_max = ln(late_od_max)) %>%
  mutate(ln_early_log_max = ln(early_od_max)) %>%
  mutate(gr_constant_max = ((ln_late_log_max) - (ln_early_log_max)) / time_diff_max) %>%
  mutate(gr_max = 0.6931 / gr_constant_max)  %>%
  select(strain, temp, gr_max)

gr_df_min <- gr_df %>% mutate(time_diff_min = late_time_min - early_time_min) %>%
  mutate(ln_late_log_min = ln(late_od_min)) %>%
  mutate(ln_early_log_min = ln(early_od_min)) %>%
  mutate(gr_constant_min = ((ln_late_log_min) - (ln_early_log_min)) / time_diff_min) %>%
  mutate(gr_min = 0.6931 / gr_constant_min) %>%
  select(strain, temp, gr_min)

gr_df_prime <- gr_df %>% left_join(gr_df_max) %>% 
  left_join(gr_df_min) %>%
  select(strain, temp, gr, gr_max, gr_min) %>%
  left_join(just_ave_lag) %>%
  select(-lag_error)

gr_df %>% ggplot() +
  geom_line(aes(x = temp, y = gr, color = strain, group = strain))


```


```{r, fig.width=10}
cols = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F", "#E5C494", "#B3B3B3")


```


```{r}
dont_make_507 <- make_all_the_things[!(make_all_the_things$strain == "507"), ]

p11 <- dont_make_507 %>% ggplot() +
  geom_line(aes(x = time, y = od, color = strain), size = 1) +
  facet_wrap(~temp) +
  theme_bw() +
  xlab("Time (hrs)")+
  ylab("Optical Density (600nm)")+
  labs(color = "Strain") +
  #ggtitle("V. alginolyticus strains vs. temperature")+
    scale_color_manual(values = cols)+
  scale_y_continuous(breaks = seq(0, 1.45, 0.5), limits = c(0, 1.45))



p11

p44 <- dont_make_507 %>% ggplot() +
  geom_line(aes(x = time, y = od, color = temp), size = 1) +
  facet_wrap(~strain) +
  theme_bw() +
  xlab("Time (hrs)")+
  ylab("Optical Density (600nm)")+
  labs(color = "Strain") +
  #ggtitle("V. alginolyticus strains vs. temperature")+
    #scale_color_manual(values = cols)+
  scale_y_continuous(breaks = seq(0, 1.45, 0.5), limits = c(0, 1.45))



p44
```


# ```{r}
# average_od <- stat_phase %>% select(c(strain, od)) %>%
#   group_by(strain) %>%
#   summarize_if(is.numeric, mean) %>%
#   ungroup() %>%
#   rename(ave_od = od)
# 
# od_diff_plot <- stat_phase %>% left_join(average_od) %>%
#   select(strain, temp, od, ave_od) %>%
#   group_by(strain, temp) %>%
#   mutate(od_diff = od - ave_od) %>%
#   mutate(error = stderr(od_diff)) %>%
#   summarize_if(is.numeric, mean) %>%
#   ungroup() %>%
#   mutate(max_od = od_diff + error,
#          min_od = od_diff - error)
# 
# ```
# ```{r}
# average_time <- lag_phase %>% select(c(strain, time)) %>%
#   group_by(strain) %>%
#   summarize_if(is.numeric, mean) %>%
#   ungroup() %>%
#   rename(ave_time = time)
# 
# 
# time_diff_plot <- lag_phase %>% left_join(average_time) %>%
#   select(strain, temp, time, ave_time) %>%
#   group_by(strain, temp) %>%
#    mutate(time_diff = time - ave_time) %>%
#   mutate(error = stderr(time_diff)) %>%
#   summarize_if(is.numeric, mean) %>%
#   ungroup() %>%
#   mutate(max_time = time_diff + error,
#          min_time = time_diff - error)
# 
# cols = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3", "#A6D854", "#FFD92F", "#E5C494", "#B3B3B3", "red")
# 



```{r, fig.width=10}
# od_diff_plot$strain <- factor(od_diff_plot$strain, levels = c("ATCC", "507", "580", "551"))
# 
# p11<- od_diff_plot %>% ggplot() +
#   geom_bar(aes(x = strain, y = od_diff, fill = temp), stat = "identity", position = position_dodge(), width = 0.75)+
#   geom_errorbar(aes(x = strain, ymax = max_od, ymin = min_od, fill = temp), 
#                  position = position_dodge(width = 0.75), size = 1, width = 0.5, alpha = 0.5) +
#   geom_text(aes(x = strain, y = od_diff + 0.02 * sign(od_diff), fill = temp, 
#                                        label = round(od_diff, 1)), position = position_dodge(width = 0.75), size = 3)+
#   coord_flip() + 
#   geom_vline(xintercept = 1.5, linetype = "dashed")+
#   geom_vline(xintercept = 2.5, linetype = "dashed")+
#   geom_vline(xintercept = 3.5, linetype = "dashed")+
#   theme_classic()+ 
# #  scale_x_reverse()+
#  # scale_y_continuous(breaks = seq(-0.75, 0.75, 0.2), limits = c(-0.75, 0.75)) +
#   ylab("Optical Density Difference (600nm)")+
#   xlab("Strain ID")+
#   labs(fill = "Temperature")+
#     scale_fill_manual(values = cols)+
#   ggtitle("Stationary Phase Optical Density vs. Temperature (c)")
# 
# p11
```

```{r, fig.width=10}
# p22 <- time_diff_plot %>% ggplot() +
#   geom_bar(aes(x = strain, y = time_diff, fill = temp), stat = "identity", position = position_dodge(), width = 0.75)+
#   geom_errorbar(aes(x = strain, ymax = max_time, ymin = min_time, fill = temp), 
#                  position = position_dodge(width = 0.75), size = 1, width = 0.5, alpha = 0.5) +
#   geom_text(data = time_diff_plot, aes(x = strain, y = time_diff + 0.2 * sign(time_diff), fill = temp, 
#                                        label = round(time_diff, 1)), position = position_dodge(width = 0.75), size = 3)+
#   coord_flip() +
#   geom_vline(xintercept = 1.5, linetype = "dashed")+
#   geom_vline(xintercept = 2.5, linetype = "dashed")+
#   geom_vline(xintercept = 3.5, linetype = "dashed")+
#   theme_classic()+
#  # scale_y_continuous(breaks = seq(-0.75, 0.75, 0.2), limits = c(-0.75, 0.75)) +
#   ylab("Time Difference (hrs)")+
#   xlab("Strain ID")+
#   labs(fill = "Temperature (C)")+
#     scale_fill_manual(values = cols)+
#   ggtitle("Duration of Lag Phase vs. Temperature (C)")
# 
# p22
```


```{r, fig.width=12}
# library(ggpubr)
# 
# ggarrange(p22, p11, ncol = 2, common.legend = TRUE)
```




```{r}
# make <- read_excel("./gr_and _lag.xlsx", 1) %>%
#   mutate(max_gr = round(max_gr, 2),
#          lag_time = round(lag_time, 2))
# 
# make2 <- read_excel("./gr_and _lag.xlsx", 2) %>%
#   mutate(max_gr = round(max_gr, 2),
#          lag_time = round(lag_time, 2))
# 
# make3 <- make
# make3$temp <- as.factor(as.numeric(make3$temp))
# 
# make %>% ggplot() +
#   geom_point(aes(x = temp, y = max_gr)) +
#   geom_line(aes(x = temp, y = max_gr), size =2) +
#   scale_fill_manual(values = cols) +
#   scale_x_continuous(breaks = seq(24, 40, 2), limits = c(24, 40))+
#   theme_bw() +
#   xlab("Temperature (C)") +
#   ylab("Fastest Doubling Time")
# 
# 
# make %>% ggplot() +
#   geom_bar(aes(x = temp, y = lag_time, fill = temp), stat = "identity")

```


```{r}
minus_507 <- gr_df_prime[!(gr_df$strain == "507"), ]

use <- minus_507 

use1 <- use %>% select(-strain) %>%
  group_by(temp) %>%
  mutate(gr_error = stderr(gr),
         lag_error = stderr((lag_time))) %>%
  summarize_if(is.numeric, mean) %>%
  ungroup() %>%
  mutate(max_gr = gr + gr_error,
         min_gr = gr - gr_error,
         max_lag = lag_time + lag_error,
         min_lag =lag_time - lag_error) %>%
  mutate(tag = "dude")


```



```{r}

p1 <- use %>% ggplot() +
  geom_point(aes(x = temp, y = gr, color = strain)) +
  geom_line(aes(x = temp, y = gr, group = strain, color = strain)) +
  geom_errorbar(aes(x = temp, ymax = gr_max, ymin = gr_min, color = strain), width = 0.4) +
  scale_fill_manual(values = cols) +
  theme_bw() +
  xlab("Temperature (C)") +
  ylab("Doubling Time (min)")+
  labs(color = "Strain")+
  geom_vline(xintercept = 4, linetype = "dashed", color = "black")+
  geom_vline(xintercept = 7, linetype = "dashed", color = "black")

p1

p2<- use %>% ggplot() +
  geom_point(aes(x = temp, y = lag_time, color = strain)) +
  geom_line(aes(x = temp, y = lag_time, group = strain, color = strain)) +
  geom_errorbar(aes(x = temp, ymax = max_lag, ymin = min_lag, color =strain), width = 0.4) +
  scale_fill_manual(values = cols) +
  theme_bw() +
  xlab("Temperature (C)") +
  ylab("Duration of Lag Time (hrs)")+
  labs(color = "Strain")+
  geom_vline(xintercept = 4, linetype = "dashed", color = "black")+
  geom_vline(xintercept = 7, linetype = "dashed", color = "black")


p2

```


```{r, fig.height=7, fig.width=6}

library(ggpubr)
ggarrange(p1, p2, ncol = 1, align = "hv")
```


```{r}
p1 <- use %>% ggplot() +
  geom_point(aes(x = temp, y = gr, color = strain)) +
  geom_line(aes(x = temp, y = gr, group = strain, color = strain)) +
  geom_errorbar(aes(x = temp, ymax = gr_max, ymin = gr_min, color = strain), width = 0.4) +
  scale_fill_manual(values = cols) +
  theme_bw() +
  xlab("Temperature (C)") +
  ylab("Doubling Time (min)")+
  labs(color = "Strain")

p1

p2<- use %>% ggplot() +
  geom_point(aes(x = temp, y = lag_time, color = strain)) +
  geom_line(aes(x = temp, y = lag_time, group = strain, color = strain)) +
  geom_errorbar(aes(x = temp, ymax = max_lag, ymin = min_lag, color =strain), width = 0.4) +
  scale_fill_manual(values = cols) +
  theme_bw() +
  xlab("Temperature (C)") +
  ylab("Duration of Lag Time (hrs)")+
  labs(color = "Strain")


p2

```

```{r}
saveRDS(use, "./temp_FINAL.rds")
```

```{r}
library(FSA)
options(digits = 4)

print("551")
lag_551 <- lag_phase %>% subset(strain == "551")
shapiro.test(lag_551$time)
kruskal.test(time ~ temp, data = lag_551)
dunnTest(lag_551$time ~ lag_551$temp, method = "holm")
```


```{r}
print("580")
lag_580 <- lag_phase %>% subset(strain == "580")
shapiro.test(lag_580$time)
kruskal.test(time ~ temp, data = lag_580)
dunnTest(lag_580$time ~ lag_580$temp, method = "holm")

```

```{r}
print("ATCC")
lag_atcc <- lag_phase %>% subset(strain == "ATCC")
shapiro.test(lag_atcc$time)
kruskal.test(time ~ temp, data = lag_atcc)
dunnTest(lag_atcc$time ~ lag_atcc$temp, method = "holm")
```

```{r}
early_log_range <- binned %>% select(-total_hits, -total_min, -reading, -time) %>%
  subset(od <= 0.2) %>%
  rename(early_log_od = od, 
         early_log_min = reading_min)

late_log_range <- binned %>% select(-total_hits, -total_min, -reading, -time) %>%
  subset(od > 0.65) %>%
  rename(late_log_od = od,
         late_log_min = reading_min) 

gr_df_range <- left_join(early_log_range, late_log_range)

gr_df_all_range <- gr_df_range %>% mutate(time_diff = late_log_min - early_log_min) %>%
  mutate(ln_late_log = ln(late_log_od)) %>%
  mutate(ln_early_log = ln(early_log_od)) %>%
  mutate(gr_constant = ((ln_late_log) - (ln_early_log)) / time_diff) %>%
  mutate(gr = 0.6931 / gr_constant) %>%
  select(strain, temp, gr)

```


```{r}
print("551")

gr_551 <- gr_df_all_range %>% subset(strain == "551") %>% na.omit()
shapiro.test(gr_551$gr)
kruskal.test(gr ~ temp, data = gr_551)
dunnTest(gr_551$gr ~ gr_551$temp, method = "holm")
```

```{r}
print("580")

gr_580 <- gr_df_all_range %>% subset(strain == "580") %>% na.omit()
shapiro.test(gr_580$gr)
kruskal.test(gr ~ temp, data = gr_580)
dunnTest(gr_580$gr ~ gr_580$temp, method = "holm")
```

```{r}
print("ATCC")

gr_atcc <- gr_df_all_range %>% subset(strain == "ATCC") %>% na.omit()
shapiro.test(gr_atcc$gr)
kruskal.test(gr ~ temp, data = gr_atcc)
dunnTest(gr_atcc$gr ~ gr_atcc$temp, method = "holm")
```



